Staying Hydrated: The Molecular Journey of Gaseous Sulfur Dioxide to a Water Surface

### 2012-03-27 resubmission/Article.tex
more revisions. Need to work on rewriting data analysis

In this study we use ab initio quantum molecular dynamics (MD) techniques to model and simulate the hydrating structures that form around a surface-bound \suldiox~on water. We simulate a dynamic water surface, complete with all the extended hydrogen-bonding interactions that capture the variability of the \suldiox~hydrate structures, and the behavior of the water surface molecules. The quantum MD technique described herein allows more accurate and realistic simulation than our previous classical MD.\cite{Shamay2011} It is also superior to small cluster DFT studies because it does not assume geometry optimized configurations, and the extended interactions of a water slab are incorporated. In our previous classical MD study we determined net orientational behavior of \suldiox~binding to a water surface, and the orientation of the waters as they respond to the presence of an adsorbing gas. Understanding the orientational behavior of molecules in the aqueous interfacial region during adsorption was a necessary first step to understanding the specific details of gas-binding and surface behavior.

@@

We believe this to be the first temperature study using quantum MD to study the binding of small gas molecules on a water surface. We show how temperature affects the bonding behavior of the surface-adsorbed \suldiox~to neighboring waters, and propose a sequential binding mechanism for \suldiox~adsorbing to a water surface. We also examine \suldiox~binding behavior when bound to the surface waters. Lastly, our analysis of a specific bonding arrangement demonstrates an extended bonding structure of \suldiox~hydrates, as they are seen to preferentially form an extended cyclic ring structure through intermolecular bonds.

>>>>

In this study we use ab initio quantum molecular dynamics (MD) techniques to model and simulate the hydrating structures that form around a surface-bound \suldiox~on a water cluster surface. We simulate a dynamic water surface of a small cluster, complete with all the extended hydrogen-bonding interactions that capture the variability of the \suldiox~hydrate structures, and the behavior of water's surface molecules. The quantum MD technique described herein allows more accurate and realistic simulation than our previous classical MD.\cite{Shamay2011} It is also superior to small cluster DFT studies because it does not assume geometry optimized configurations, and the extended interactions of a larger water cluster are incorporated. In our previous classical MD study we determined net orientational behavior of \suldiox~binding to a water surface, and the orientation of the waters as they respond to the presence of an adsorbing gas. Understanding the orientational behavior of molecules in the aqueous interfacial region during adsorption was a necessary first step to understanding the specific details of gas-binding and surface behavior.

@@

We believe this to be the first temperature study using quantum MD to study the binding of small gas molecules on a water surface. We show how temperature affects the bonding behavior of the surface-adsorbed \suldiox~to neighboring waters, and propose a sequential binding mechanism for \suldiox~adsorbing to a water surface. We also examine \suldiox~binding behavior when bound to the surface waters. Lastly, our analysis of a specific bonding arrangement demonstrates an extended bonding structure of \suldiox~hydrates, as they are seen to form an extended cyclic ring structure through intermolecular bonds.
